\textcolor{black}{In-silico molecular transport via perivascular networks in the human intracranial space}

### 2025-06-26 paper/main.tex
Minor edits in the main text after reading through the diff.
Reduced -> changed

\title{\textcolor{blue}{In-silico molecular transport via perivascular networks in the human intracranial space}}
\author[1]{Marius Causemann}
\author[1]{Miroslav Kuchta}
\author[2]{Rami Masri}
\author[1,3,*]{Marie E. Rognes }
\affil[1]{Department of Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway}
\affil[2]{Division of Applied Mathematics, Brown University, Providence, Rhode Island, USA}
\affil[3]{K. G. Jebsen Centre for Brain Fluid Research, University of Oslo, Norway}
\affil[*]{meg@simula.no}

@@

Now, to examine how CSF pulsatility affects the tracer enrichment patterns,
we consider three variations of the baseline: (i) no CSF production,
(ii) reduced pulsatility and thus decreased dispersion, and (iii) higher pulsatility with increased dispersion. We computed the reduced and increased pulsatility scenarios by halving and doubling the inflow rates associated with both cardiac and respiratory pulsations, which reduced the dispersion factors by 0.25$\times$ and 4$\times$, respectively. Note that behaviour directly reflects the nature of our model: Stokes flow is linear in its inflow boundary conditions, and the diffusion enhancement factor is quadratic in the predicted pressure gradient.
Without CSF production, transport is considerably delayed
(\Cref{fig:csf}N, O). Even after $12$ hours, tracer remains in the
subtentorial regions around the cerebellum, the brain stem and in the
surrounding CSF. Interestingly, the lack of CSF production instead
allows tracer to travel upwards through the ventricular system,
reaching the third ventricle after around $12$ hours. On the other
hand, if the CSF pulsatility is reduced, we observe rapid transport
towards the upper convexity of the cranium, as in the baseline model,
but the tracer spreads exclusively within the anterior regions
(\Cref{fig:csf}P). This feature can be attributed to the CSF flow
bifurcation posterior to the ambient cistern (\Cref{fig:csf}D):
without sufficient diffusion, the tracer is unable to cross into the
posterior SAS. Indeed, with higher dispersion, the tracer moves
through the quadrigeminal cistern and further upwards into the
longitudinal fissure, with also enrichment of the cerebellum
(\Cref{fig:csf}Q).

@@

    computed/estimated within this work. The diffusion coefficients

>>>>

\title{\textcolor{black}{In-silico molecular transport via perivascular networks in the human intracranial space}}
\author[1]{Marius Causemann}
\author[1]{Miroslav Kuchta}
\author[2]{Rami Masri}
\author[1,3,*]{Marie E. Rognes }
\affil[1]{Department of Numerical Analysis and Scientific Computing, Simula Research Laboratory, Oslo, Norway}
\affil[2]{Division of Applied Mathematics, Brown University, Providence, Rhode Island, USA}
\affil[3]{K. G. Jebsen Centre for Brain Fluid Research, University of Oslo, Norway}
\affil[*]{meg@simula.no}

@@

Now, to examine how CSF pulsatility affects the tracer enrichment patterns,
we consider three variations of the baseline: (i) no CSF production,
(ii) reduced pulsatility and thus decreased dispersion, and (iii) higher pulsatility with increased dispersion. We computed the reduced and increased pulsatility scenarios by halving and doubling the inflow rates associated with both cardiac and respiratory pulsations, which changed the dispersion factors by 0.25$\times$ and 4$\times$, respectively. Note that behaviour directly reflects the nature of our model: Stokes flow is linear in its inflow boundary conditions, and the diffusion enhancement factor is quadratic in the predicted pressure gradient.
Without CSF production, transport is considerably delayed
(\Cref{fig:csf}N, O). Even after $12$ hours, tracer remains in the
subtentorial regions around the cerebellum, the brain stem and in the
surrounding CSF. Interestingly, the lack of CSF production instead
allows tracer to travel upwards through the ventricular system,
reaching the third ventricle after around $12$ hours. On the other
hand, if the CSF pulsatility is reduced, we observe rapid transport
towards the upper convexity of the cranium, as in the baseline model,
but the tracer spreads exclusively within the anterior regions
(\Cref{fig:csf}P). This feature can be attributed to the CSF flow
bifurcation posterior to the ambient cistern (\Cref{fig:csf}D):
without sufficient diffusion, the tracer is unable to cross into the
posterior SAS. Indeed, with higher dispersion, the tracer moves
through the quadrigeminal cistern and further upwards into the
longitudinal fissure, with also enrichment of the cerebellum
(\Cref{fig:csf}Q).

@@

    computed/estimated within this work. The diffusion coefficient
